On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-06-25 docs/mvfits_paper/mvf.tex
adding new models for QNM frequencies of Kerr, adding functions for Kerr Light-Ring and ISCO radii and frequencies
adding reference for ysmodel training data
moving citation of LIGO systematics paper

In this context, signal detection and subsequent inference of physical parameters hinges upon efficient models for source properties and dynamics \cite{Abbott:2016wiq}.

@@

As the merger of isolated \bh{s} is expected to result in a perturbed Kerr \bh{}, there is related interest in having accurate and computationally efficient models for perturbative parameters, namely those that enable evaluation of the related \rd{} radiation \cite{Berti:2005ys,TheLIGOScientific:2016wfe}.

@@

@@

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% %
\newpage
% \bibliographystyle{ieeetr}
\bibliographystyle{mnras}
\bibliography{mvf.bib}
\end{document}

>>>>

In this context, signal detection and subsequent inference of physical parameters hinges upon efficient models for source properties and dynamics \cite{Abbott:2016wiq,TheLIGOScientific:2016wfe}.

@@

As the merger of isolated \bh{s} is expected to result in a perturbed Kerr \bh{}, there is related interest in having accurate and computationally efficient models for perturbative parameters, namely those that enable evaluation of the related \rd{} radiation \cite{Berti:2005ys}.

@@

We note that the related training data is available online at reference~\cite{ys_training_data}.

@@

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% %
\newpage
% \bibliographystyle{ieeetr}
% \bibliographystyle{mnras}
\bibliography{mvf.bib}
\end{document}
